---
title: "OSP partitions check"
author: "Susana Proenca"
format: html
editor: visual
---

## Evaluation of PK-Sim partition coefficients

## Introduction

This workflow is to evaluate the OSP partition algorithms.

We are using the experimental partitioning values collected in Utsey et al, where they also report their input parameters. \[NEED TO KNOW HOW PARTITIONS WERE DERIVED, IN VIVO OR EX VIVO\]

\*for now I am excluding zwitterions. Need better curation of data to include them.

### To do

-   include blood-cells partitioning

-   possibility correcting fraction unbound

-   get ionization included

-   make plots for every tissue with different lipophilicity

-   make conclusions

-   see overlap list chemicals with ONTOX-DNT and INOTIV-DNT

## Running Code

Per tissue where we have partitioning data and with two options for input lipophlciity we can get the correlation plots but also the calculated R2 , also for different groups of chemicals.

Since the logMA was not available for many chemicals we use the same linear regression from Yu et al that was used in Ans Punt models and in Rene HTP.

```{r}

source("partition check/function_plots_partition.R")

#run the models
  Berez_model<-Rat_model("Berez",lipophilicity)
  PK_Sim_model<-Rat_model("PKSim",lipophilicity)
  Poulin_model<-Rat_model("Poulin",lipophilicity)
  RR_model<-Rat_model("Rodger_Rowland",lipophilicity)
  Schmitt_model<-Rat_model("Schmitt",lipophilicity)
  
plot_tissue("Lung",lipophilicity="LogP")

```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

### DNT chemicals

For the DNT chemicals in ONTOX and INOTIV -colb that have brain data plot them here.
